\fontsize{18}{22}\selectfont A comprehensive study of the phylodynamics of SARS-CoV-2 in Europe

### 2021-03-03 reports/mt-thesis/methods.tex
wip methods

\section{SARS-CoV 2 genome data set}

@@

\section{The multitype birth death model}

@@

We parameterize our model in terms of the effective reproductive number $R_i = \frac{\lambda_i}{\mu_i + \psi_i}$, a key value in epidemic control and understanding, the rate of becoming uninfectious $\delta_i = \mu_i + \psi_i$ and the probability of and individual to be sequenced $s_i = \frac{\psi_i}{\mu_i + \psi_i}$.

\section{Epidemic trajectories and structured trees}

@@

\section{BDMM-Prime Inference}

@@

@@

\section{Modeling the early dynamics of SARS-CoV-2 in Europe}

@@

\section{Incorporating travel data}

\section{GLM predictos data}

\section{Bayesian inference of phylodynamic parameters}

@@

\subsubsection{R0}
R0 constant except for China (and Italy? maybe not in the main analysis).

@@

\section{Processing of epidemic trajectories}
In our case, for each set of parameters and tree we will simulate 10000 trajectories with an epsilon of 0.3 and select one of them with importance sampling.
We have one trtajectory for each step in the MCMC. We subsampled x.

\section{Data availability}
GISAID data table.

\section{Code availability and analyses reproducibility}
All the code is availables at ...
We have implement the full workflow with Snakemake so its fully reproducible.

>>>>

\textbf{SARS-CoV 2 genome data set}

@@

\textbf{The multitype birth death model}

@@

We parameterize our model in terms of the effective reproductive number $R_i = \frac{\lambda_i}{\mu_i + \psi_i}$, a key value in epidemic control and understanding, the rate of becoming uninfectious $\delta_i = \mu_i + \psi_i$ and the probability of and individual to be sequenced $s_i = \frac{\psi_i}{\mu_i + \psi_i}$.\\

\textbf{Epidemic trajectories and structured trees}

@@

\textbf{BDMM-Prime Inference}

@@

While it is possible to do it in the same step \cite{epiestim} it is very slow and computationally expensive. With these two step analyses implmented in BDMM-Prime \cite{bdmm-primegit} the epidemic trajectory inference has almost no overcost and we obtain the same result.

@@

\textbf{Incorporating travel data}

GLM predictos data

\textbf{Model specifications and priors}

@@

@@

R0 constant except for China (and Italy? maybe not in the main analysis).

@@

\textbf{Processing of epidemic trajectories}
In our case, for each set of parameters and tree we will simulate 10000 trajectories with an epsilon of 0.3 and select one of them with importance sampling.
We have one trtajectory for each step in the MCMC. We subsampled x.

\textbf{Data availability}
GISAID data table.

\textbf{Code availability and analyses reproducibility}
All the code is availables at ...
We have implement the full workflow with Snakemake so its fully reproducible.
